\Large \bf 6.824 Final Project

### 2014-05-11 writeup/paper.tex

>>>>

When one server contacts another via the FetchRecovery RPC, both
servers enter a recovering state. This state means that neither are
allowed to modify their databases \emph{except} through the recovery
process. Depending on how many replicas there are, this may render a
replica group unable to process requests while recovery is underway.
If there are enough replicas so that paxos majority can still be
reached, then the recovering servers will catch up once they come back
online, using the functionality already built in to sync lagging paxos
servers.

All recovery processes send over both the relevant portions of the k/v
store, as well as paxos state and any state needed to detect
duplicates.

\textbf{Single server crashing and restarting, disk in-tact}: The
recovery process contacts a random replica in the same replica group.
The recovering server tells the up-to-date server its current state,
and the up-to-date server responds with any state the recoverer is
missing. This works because the server only discards old decisions if
all participants have marked that sequence number as 'done'.

\textbf{Single server crashing and disk lost}: The recovery process
contacts a random replica in the same replica group, and tells the
up-to-date server that it has no state. The two servers open an
auxillary TCP connection to send over the relevant portions of the
database. This avoids RPC overhead, since the database might be large.
The database has an in-order iterator, in case the TCP connection
fails, the recoverer can re-establish the connection and ask the
sender to pick up where it left off. If the sending server fails, then
the recovering server asks a new replica. This allows for a failure
mode where the original server remians locked permanently. We have
decided that this is preferable to sacrificing consistency, and the
system administartor can resolve the problem by rebooting the hing
server.

\textbf{Complete crash of all servers}: If all servers lose their disk
state, then all will restart and begin like a brand new deployment. If
the disks are not lost, then the recovery process will read the paxos
state written to disk and pick up where it left off. Because we write
to disk before any operation commits, data is not lost.

We use leveldb. To guarantee persistence, we enforce writing to disk
all operations before returning. This slows performance down, but
prevents loss of data that the client wants committed. Speed could be
gained using a Harp-like set of pointers, but this would be
complicated and the client would have to understand the modified
persistence model.
